Supporting Information: Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-09-01 paper/submissions/nature/supp.tex
Add full paper files

We examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network. We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight given by the sum of the co-occurences over all researchers. and edges are co-occurrence between two organizations. The Personalized Page Rank is a ranking algorithm for nodes based on a random walk process on networks.
The walker visiting at a node moves to a neighboring node chosen randomly with a probability proportionally to the weight of the edge in one step. Furthermore, with probability $\alpha$, the walker is teleported back to the starting node. The rank of a node is determined by the probability that the walker visits the node in the stationary state. The stationary distribution of the random walker starting from node $i$, denoted by $p_i=(p_{ik})$, is given by

\begin{equation}
	\label{eq:ppr}
	p_i = (1 - \alpha) W p_i +  \alpha v_i 
\end{equation}
where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted transition matrix of the unbiased random walker. We used $\alpha=0.9$ here.

>>>>

We examine the gravity model on the Personalized Page Rank (PPR)\autocite{jeh2003scaling} as a benchmark on the network. We construct the co-occurrence network of $N$ organizations, in which each edge between organizations $i$ and $j$ represents a co-occurence of $i$ and $j$ in the same affiliation trajectory, with weight $W_{ij}$ given by the sum of the co-occurences over all researchers. and edges are co-occurrence between two organizations. The Personalized Page Rank is a ranking algorithm for nodes based on a random walk process on networks.
The walker visiting at a node moves to a neighboring node chosen randomly with a probability proportionally to the weight of the edge in one step. Furthermore, with probability $\alpha$, the walker is teleported back to the starting node. The rank of a node is determined by the probability that the walker visits the node in the stationary state. The stationary distribution of the random walker starting from node $i$, denoted by $p_i=(p_{ik})$, is given by

\begin{equation}
	\label{eq:ppr}
	p_i = (1 - \alpha) v_i + \alpha p_i W,
\end{equation}
where $v_i$ is a column vector of length $N$ with entries that are all zero except the $i$th entry that equals to one, $W = (W_{ij})$ is the weighted adjacency matrix. We used $\alpha=0.9$ here.
